\documentclass[11pt,a4paper,notitlepage]{article}
\usepackage[margin=1in]{geometry}
\usepackage{algorithm,amssymb,amsmath,algpseudocode}
\usepackage{lmodern}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\input{../../tomsdefs}

\title{pASSWORD typos and\\ How To Securely Correct Them}
\author{Rahul Chatterjee}
\begin{document}
%\maketitle
\section*{Application for Conference Grant}
%\subsection*{Rahul Chatterjee}
\vspace{0.2in}

% \begin{abstract}\em
%   We provide the first treatment of typo-tolerant password
%   authentication for arbitrary user-selected passwords. Such a system,
%   rather than simply rejecting a login attempt with an incorrect
%   password, tries to correct common typographical errors on behalf of
%   the user. Limited forms of typo-tolerance have been used in some
%   industry settings, but to date there has been no analysis of the
%   utility and security of such schemes.

%   In studies conducted on Amazon Mechanical Turk and via
%   instrumentation of the production Dropbox login infrastructure, we
%   quantify the kinds and rates of typos made by users. Our experiments
%   reveal that almost 10\% of login attempts fail due to a handful of
%   simple, easily correctable typos, such as capitalization errors.  We
%   show that correcting just a few of these typos would reduce login
%   delays for a significant fraction of users as well as enable an
%   additional 3\% of users to achieve successful login.

%   We introduce a framework for reasoning about typo-tolerance, and
%   investigate the seemingly inherent tension here between security and
%   usability of passwords. We use our framework to show that there
%   exist typo-tolerant authentication schemes that can get corrections
%   for ``free'': we prove they are as secure as schemes that always
%   reject mistyped passwords. Building off this theory, we detail a
%   variety of practical strategies for securely implementing
%   typo-tolerance.
% \end{abstract}

\section{Student's Statement} 
% \texttt{ Note: An application for a travel award will consist of a
%   single PDF file with the student's resume, a statement from the
%   student indicating if they would like to attend the symposium and/or
%   the workshops (and which workshop), and a letter from the student's
%   research advisor with a justification of financial need. The
%   student's statement should also include a summary of research
%   interests, and a brief discussion of why the applicant will benefit
%   from participating in the symposium.}\\

I would like to attend the 37th IEEE \underline{Symposium} on Security
and Privacy from May 23 to May 25, 2016 at The Fairmont, San Jose, CA.

\paragraph{Research Interest.}
My primary research interest targets making password-based
authentication and encryption schemes simple, safe and easy to use.
Passwords are ubiquitous in today's web authentication. Passwords need
no specialized hardware, such as a card or finger-print reader, to
authenticate. Moreover, if a user forgets their password, it is much
easier to reset them compared to other means of authentication system
that are based on smart-cards or bio-metrics.  However, users tend to
choose easily guessable passwords, and reuse them across multiple
websites. Moreover, users complain that complex passwords are hard to
remember and difficult to enter. My research targets addressing these
concerns.

% Given that nowadays users have many online accounts, remembering
% distinct complex passwords for each of them poses severe memory
% burden on users.

The biggest problem with password based encryption schemes is that,
attackers can mount {\em offline brute-force decryption} attacks,
should they get hold of a ciphertext. The attack works by making
repeated attempts to decrypt the ciphertext with different guesses for
the password without any need to communicate with any server that is
the legitimate owner of the ciphertext. Thanks to advances in modern
password cracking tools, attacker typically guesses the correct
password within a manageable number of queries. Additionally, every
wrong guess of the password results in decryption failure, making it
clear for the attacker to figure out whether the guess is right or
wrong. I am building new password based encryption schemes that resist
offline brute-force attacks by producing plausible looking decoy
plaintexts for each of the guessed password.  This makes it harder for
the attacker to learn whether or not the decryption was successful.  A
typical use-case of password based encryption scheme is to protect
credential stores, such as password managers, where passwords of
different programs or websites are stored, and the store is encrypted
under a master-password chosen by the user.  I have designed a new
generation credential store that aids offline cracking resistance, and
now I am exploring options to apply that technique to other places
where password based encryption is used.


To prevent passwords from being easily guessable, many security
experts advise users to choose {\em long and complex} passwords, which
have to be reproduced exactly every time they wish to log in. Long and
complex passwords are hard to remember as well as are time consuming
and error prone to type. This is worse if the user is using a
touchscreen device to log in. All this, in turn, discourages users
from choosing strong passwords.  Allowing small typographical errors
in passwords might alleviate these problems, but it is not clear,
upfront, how to perform typo-tolerance, and what is the effect on
security of this.  I am doing studies to quantify the usability and
security impact of tolerating small errors while entering
passwords. Our initial study reveals that a significant fraction of
users failed to log in or faced a delay in login due to a handful of
easily correctable typographical errors, while, if carefully
constructed, typo tolerance would not degrade security by more than a
negligible amount.  % The biggest challenge in analyzing typos in
% passwords is to collect real world typo data.
I am also looking into allowing typo tolerance in different contexts
where human-chosen passwords are used, such as password authenticated
key exchange, and perform more thorough analysis of security.
\\

% Why want to join the conference?
\paragraph{Reasons to join the symposium.}
IEEE S\&P is one of the best conferences in the field of security and
privacy. Above all, I am happy and excited to be able to present my
work in front of the experts in the field, and get valuable feedback
from them.  Attending this conference as a first year graduate
student, I will have ample networking opportunities. This will enable
me to build strong relationships with the members of the vibrant
community and broaden my scope to collaborate with other
researchers. To know and get known in the research community is
important for succeeding in graduate studies. Attending first tier
conferences, such as IEEE S\&P, will greatly help me to do so.


\section{Advisor's Note}
Rahul is going to present his work titled ``pASSWORD tYPOS and How to
Correct Them Securely'' at the 37th IEEE Symposium on Security and
Privacy. This is a very interesting work showing the benefits of
fixing typographical mistakes in passwords. Also, this work proposes
ways to securely correct typos, that has minimal security degradation
with respect to traditional password checkers that do not allow typos
in password submissions.

Attending this conference will be greatly beneficial for Rahul's
graduate studies as well as help him building research relationships
with the members of the community.  Moreover, obtaining the conference
grant will boost the confidence of a new researcher like Rahul, and
encourage him to continue working on challenging problems in security
and privacy that has larger impact on the society.

\input{resume}




\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
